\subsection{Fraction of time spent in different parts of the project}

\begin{itemize}
    \item Analysis of various string matching algorithms : To get started with the project, we explored plagiarism detector software and their workings. MOSS is widely used plagiarism detector software. It is currently used by many institutes to check plagiarism over programming assignments and projects.  \\
    MOSS\cite{moss} makes it possible to objectively and automatically check all program
solutions for evidence of copying. MOSS works with programs written in C, C++, Java, Pascal, Ada and other languages and looks out for similar code structure in different documents.When someone changes the variable name or tries to introduce white spaces, some random code to deceive it, it typically does not work in their favor as the structure of the program is unchanged,while the number of token and line matches between the documents is still the same. \\
For this project we are just working on objective and subjective type of matches. We explored strsim library which implements various string similarity algorithms.
    \item Implementation of algorithm : We are using weighted combination of best performance algorithms for our task and trying to come up with an accurate and fair plagiarism index between all pairs of responses.
    \item Front and Back end development : We used wordpress for designing website for our test interface. We used Wordpress plugin Ninja for the formation of any new test.
\end{itemize}


\subsection{Fraction of work done by different team members}       
All the 3 team members contributed equally in the project with full dedication.