\subsection{Python} 
Python is a high-level, interpreted and general-purpose dynamic programming language that focuses on code readability. The syntax in Python helps the programmers to do coding in fewer steps as compared to Java or C++.The Python is widely used in bigger organizations because of its multiple programming paradigms. They usually involve imperative and object-oriented functional programming. It has a comprehensive and large standard library that has automatic memory management and dynamic features.\cite{python}\\ \\
Python has top the charts in the recent years over other programming languages like C, C++ and Java and is widely used by the programmers. The software development companies prefer Python language because of its versatile features and fewer programming codes. Nearly 14\% of the programmers use it on the operating systems like UNIX, Linux, Windows and Mac OS. The programmers of big companies use Python as it has created a mark for itself in the software development with characteristic features like-
\begin{itemize}
    \item Interactive
    \item Interpreted
    \item Modular
    \item Dynamic
    \item Object-oriented
    \item Portable
    \item High level
    \item Extensible in C++ and  C
\end{itemize}
\subsection{Wordpress}
WordPress is a simple and free Content Management System with numerous features and ample customization possibilities. It can be used to develop any kind of website, be it for a small business or for a large enterprise. \cite{word} \\ \\
Following featurs are very impressive benifits of wordpress : 
\begin{itemize}
    \item WordPress Is A Universal Platform
    \item Easy To Use
    \item Easy To Set-up
    \item  Easy To Update
    \item  Easy To Manage
    \item WordPress Is Reliable
    \item Provides Greater Accessibility
    \item Provides plugin features
\end{itemize}
\subsection{MySQL}
MySQL is a relational database management system based on SQL – Structured Query Language. The application is used for a wide range of purposes, including data warehousing, e-commerce, and logging applications. The most common use for mySQL however, is for the purpose of a web database. \cite{sql}\\
In association with a scripting language such as PHP or Perl (both offered on our hosting accounts) it is possible to create websites which will interact in real-time with a mySQL database to rapidly display categorised and searchable information to a website user.
